Missing the Point\(\colon\) Non-Convergence in Multiple Imputation Procedures

### 2020-03-31 3.Thesis/1.SimulationStudy/Writeup/manuscript.Rmd
Ran with 25 and 50% missingness

---
title: Missing the Point$\colon$ Non-Convergence in Multiple Imputation Procedures
runninghead: Oberman
author:
- name: H. I. Oberman
  num: 1
address:
- num: 1
  org: Department of Methodology and Statistics, Utrecht University, Utrecht, The Netherlands
corrauth: "Hanne Oberman, Sjoerd Groenman building, Utrecht Science Park, Utrecht, The Netherlands."
email: h.i.oberman@uu.nl
abstract: "Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aenean ut elit odio. Donec fermentum tellus neque, vitae fringilla orci pretium vitae. Fusce maximus finibus facilisis. Donec ut ullamcorper turpis. Donec ut porta ipsum. Nullam cursus mauris a sapien ornare pulvinar. Aenean malesuada molestie erat quis mattis. Praesent scelerisque posuere faucibus. Praesent nunc nulla, ullamcorper ut ullamcorper sed, molestie ut est. Donec consequat libero nisi, non semper velit vulputate et. Quisque eleifend tincidunt ligula, bibendum finibus massa cursus eget."
keywords: MICE; convergence; 
classoption:
  - Royal
  - times
bibliography: thesis.bib
bibliographystyle: sageh
output:
  rticles::sage_article:
    keep_tex: yes
---

@@

and simulated with the function `mvtnorm::rmvnorm()`. Outcome variable $Y$ is subsequently calculated as 
$$Y =  2X_1 + .5X_2 - X_3 + \epsilon .$$
<!-- This note only considers a 'missing completely at random' (MCAR) mechanism, where the probability of being missing is equal for all $n \times p$ cells in $y$ [@rubin87].  -->

>>>>

---
title: Missing the Point$\colon$ Non-Convergence in Multiple Imputation Procedures
runninghead: Oberman
author:
- name: H. I. Oberman
  num: 1
address:
- num: 1
  org: Department of Methodology and Statistics, Utrecht University, Utrecht, The Netherlands
corrauth: "Hanne Oberman, Sjoerd Groenman building, Utrecht Science Park, Utrecht, The Netherlands."
email: h.i.oberman@uu.nl
abstract: "Multple imputation by chained equations (mice) is a widely used tool to accommodate missing data. While empirical evidence supports the validity of inferences obtained using mice, there is no consensus on the convergence properties of the method. This paper provides insight into non-convergence of mice algorithms."
keywords: MICE; convergence 
classoption:
  - Royal
  - times
bibliography: thesis.bib
bibliographystyle: sageh
output:
  rticles::sage_article:
    keep_tex: yes
---

@@

and simulated with the function `mvtnorm::rmvnorm()`. Outcome variable $Y$ is subsequently calculated as 
$$Y =  1 + 2X_1 + .5X_2 - X_3 + \epsilon .$$
<!-- This note only considers a 'missing completely at random' (MCAR) mechanism, where the probability of being missing is equal for all $n \times p$ cells in $y$ [@rubin87].  -->

### 2020-03-31 3.Thesis/1.SimulationStudy/Writeup/manuscript.tex
Ran with 25 and 50% missingness

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Aenean ut elit
odio. Donec fermentum tellus neque, vitae fringilla orci pretium vitae.
Fusce maximus finibus facilisis. Donec ut ullamcorper turpis. Donec ut
porta ipsum. Nullam cursus mauris a sapien ornare pulvinar. Aenean
malesuada molestie erat quis mattis. Praesent scelerisque posuere
faucibus. Praesent nunc nulla, ullamcorper ut ullamcorper sed, molestie
ut est. Donec consequat libero nisi, non semper velit vulputate et.
Quisque eleifend tincidunt ligula, bibendum finibus massa cursus eget.
\end{abstract}

\keywords{MICE; convergence;}

@@

and simulated with the function \texttt{mvtnorm::rmvnorm()}. Outcome
variable \(Y\) is subsequently calculated as
\[Y =  2X_1 + .5X_2 - X_3 + \epsilon .\]

>>>>

\begin{abstract}
Multple imputation by chained equations (mice) is a widely used tool to
accommodate missing data. While empirical evidence supports the validity
of inferences obtained using mice, there is no consensus on the
convergence properties of the method. This paper provides insight into
non-convergence of mice algorithms.
\end{abstract}

\keywords{MICE; convergence}

@@

and simulated with the function \texttt{mvtnorm::rmvnorm()}. Outcome
variable \(Y\) is subsequently calculated as
\[Y =  1 + 2X_1 + .5X_2 - X_3 + \epsilon .\]
